How to write a PhD in Biological Sciences: a guide for the uninitiated

### 2021-07-20 2.21-proposal-presentation.Rmd
Add files via upload
# After copy edits

## Making a presentation from your chapter, paper or proposal {#proposal-presentation}

@@

1. **Give yourself plenty of time to prepare**
Although your presentation might be weeks away, you are going to need ~4 weeks to get the presentation ready, run it past your advisor (and potentially other co-authors), and practice your talk. As usual, my advice is not to leave it until the last minute to prepare as you'll get out what you put in. 
2. **Know who your audience is and what they expect**
If you have no idea of who your audience will be and what they will be expecting, then attend some other talks in the same seminar series, or ask your advisor and/or other lab colleagues for input. The more cross-disciplinary your audience is, the more general you should make your talk. If you've still no idea, pitch it for a very broad audience at last year undergraduate level.
3. **Be sure of exactly how much time you will have to talk**
Be aware that your time slot might include time for questions, and so find out exactly how much talking time you have. If there is a long time set aside for discussion, you might want to throw some extra slides in that can help facilitate answering expected questions.
4. **Make sure you know the format of the presentation**
If you don't know, then you can't make any assumptions about what might be present in the room where you give your presentation. I turned up to give my talk with a presentation on a USB drive only to find that there is no computer, no projector and a room of people expecting me to entertain them for an hour. Even if you know that a projector is present, it's good to have some extra context: 
  + for example is the computer Mac, PC or Linux; 
  + should you bring your own laptop; 
  + is there a pointer; 
  + can it advance slides
  + If in doubt then bring your own accessories.
5. **Know exactly where you are giving your talk and plan for plenty of travel time**
Hopefully, you will be very familiar with the venue, and travelling to the venue will only involve a brief walk. I've made some rookie errors in the past, including deciding to cycle to the venue, getting caught in a cloudburst and arriving literally dripping wet (it was in the UK). The more comfortable you are with the whole setup, and the more organised you can be about getting yourself there without incidents, the better the talk will go for you.

Essentially, you have a story to tell, but does not mean you are story telling. It means that your presentation will require you to talk continuously for your allotted period of time, and that the sentences must follow on from each other in a logical narrative; i.e. a story.

### So where do you start?

#### Here are some simple rules to help guide you to build your presentation:

- One slide per minute: However many minutes you have to present, that’s your total number of slides. Don’t be tempted to slip in more.
- Keep the format clear: There are lots of templates available to use, but you’d do best to keep your presentation very clean and simple.
- Be careful with animations: You can build your slide with animations (by adding images, words or graphics). But do not flash, bounce, rotate or roll. No animated little clipart characters. - No goofy cartoons – they’ll be too small for the audience to read. No sounds (unless you are talking about sounds). Your audience has seen it all before, and that’s not what they’ve come for. They have come to hear about your research proposal.
- Don’t be a comedian: Everyone appreciates that occasional light-hearted comment, but it is not stand-up. If you feel that you must make a joke, make only one and be ready to push on when no-one reacts. Sarcasm simply won’t be understood by the majority of your audience, so don’t bother: unless you’re a witless Brit who can’t string three or more sentences together without [in which case you have my empathy].

#### A formula for presenting a proposal

1. You need a title slide (with your name, that of your advisor and institution)
1. Several slides of introduction
  + that put your study into the big picture
  + explain variables in the context of existing literature
  + explain the relevance of your study organisms
  + give the context of your own study
1. Your aims and hypotheses
1. Methods and Materials
  + Images of apparatus or diagrams of how apparatus are supposed to work. If you can’t find anything, draw it simply yourself.
  + Your methods can be abbreviated but the methods are important for a proposal, especially the numbers of replicates and the variables that you plan to measure from them. 
  + Analyses are important. Make sure that you understand how they work, otherwise you won’t be able to present them to others. Importantly, explain where each of the variables that you introduced, and explained how to measure, fit into the analyses. There shouldn’t be anything new or unexpected that pops up here.
1. Expected results
I like to see what the results might look like, even if you have to draw graphs with your own lines on it. Use arrows to show predictions under different assumptions.
1. Budget
1. Timeline

#### A formula for presenting a chapter or paper

1. You need a title slide (with your name, that of your advisor and/or co-authors and institution). Most institutions have logos, and they like you to use them.
1. Several slides of introduction
  + that put your study into the big picture
  + explain variables in the context of existing literature
  + explain the relevance of your study organisms
  + give the context of your own study
1. Your aims and hypotheses
1. Methods and Materials
  + You are going to have to skip details of the methods
  + Be prepared to pare this down to the important stuff
  ++ variables
  ++ replicates
  ++ analyses
  + Use diagrams and images if you can
1.Results & Discussion
  + If you have a lot of results, then it makes sense to discuss them while they are still fresh in the minds of your audience. 
  + If you had several hypotheses, then place reminders of what they are when you respond to them with the results
1. Summary 
  + state initial hypotheses and whether or not you accept them
  + give some ideas for next steps

### Know your story first, and then make your presentation

@@

Remember that you don't need to include every detail in your slides or your talk. If the audience can follow your story, but wants to know the details at the end, then they can ask questions about the details. Indeed, you can tell your audience precisely this as a way of side-stepping chunks of (especially) methodologies.

@@

### Slide layout

1. Your aim is to have your audience listen to you, and only look at the slides when you indicate their relevance. 
1. You’d be better off having slides without words, then your audience will listen instead of trying to read. As long as they are reading, they aren't listening. Really try to limit the words you have on any single slide (<30). Don’t have full sentences, but write just enough to remind you of what to say and so that your audience can follow when you are moving from point to point.
1. Use bullet pointed lists if you have several points to make (Font 28 pt)
1. If you only have words on a slide, then add a picture that will help illustrate your point. This is especially useful to illustrate your organism. At the same time, don’t have anything on a slide that has no meaning or relevance. Make sure that any illustration is large enough for your audience to see and understand what it is that you are trying to show.
1. Everything on your slide must be mentioned in your presentation, so remove anything that becomes irrelevant to your story when you practice.
1. Tables: you are unlikely to have large complex tables in a presentation, but presenting raw data or small words in a table is a way to lose your audience. Make your point in another way.
1. Use citations (these can go in a smaller font: 20 pt). I like to cut out the title and authors of the paper from the pdf and show it on the slide.
1. If you can, have some banner that states where you are in your presentation (e.g. Methods, or 5 of 13). It helps members of the audience who might have been daydreaming.

@@

### Practice, practice, practice

1. It can’t be said enough that you must practice your presentation. Do it in front of a mirror in your bathroom. In front of your friends. It's the best way of making sure you'll do a good job.
1. If you can't remember what you need to say, write flash cards with prompts. Include the text on your slide and expand. When you learn what’s on the cards, relate it to what’s on the slide so that you can look at the slides and get enough hints on what to say. Don’t bring flashcards with you to your talk. Instead be confident enough that you know them front to back and back to front.
1. Practice with a pointer and slide advancer (or whatever you will use in the presentation). You should be pointing out to your audience what you have on your slides; use the pointer to do this.
1. Avoid taking anything with you that you might fiddle with.

>>>>

# Making a presentation from your chapter, paper or proposal {#proposal-presentation}

@@

1. **Give yourself plenty of time to prepare**
Although your presentation might be weeks away, you are going to need ~4 weeks to get the presentation ready, run it past your advisor (and potentially other co-authors), and practice your talk. As usual, my advice is not to leave it until the last minute to prepare as you'll get out what you put in. 
2. **Know who your audience is and what they expect**
If you have no idea of who your audience will be and what they will be expecting, then attend some other talks in the same seminar series, or ask your advisor and/or other lab colleagues for input. The more cross-disciplinary your audience is, the more general you should make your talk. If you've still no idea, pitch it for a very broad audience at last year undergraduate level.
3. **Be sure of exactly how much time you will have to talk**
Be aware that your time slot might include time for questions, and so find out exactly how much talking time you have. If there is a long time set aside for discussion, you might want to throw some extra slides in that can help facilitate answering expected questions.
4. **Make sure you know the format of the presentation**
If you don't know, then you can't make any assumptions about what might be present in the room where you give your presentation. I turned up to give my talk with a presentation on a USB drive only to find that there was no computer, no projector and a room of people expecting me to entertain them for an hour. Even if you know that a projector is present, it's good to have some extra context: 
  + for example is the computer Mac, PC or Linux; 
  + should you bring your own laptop; 
  + is there a pointer; 
  + can it advance slides
  + if in doubt, then bring your own accessories.
5. **Know exactly where you are giving your talk and plan for plenty of travel time**
Hopefully, you will be very familiar with the venue, and travelling to the venue will only involve a brief walk. I've made some rookie errors in the past, including deciding to cycle to the venue, getting caught in a cloudburst and arriving literally dripping wet (it was in the UK). The more comfortable you are with the whole setup, and the more organised you can be about getting yourself there without incidents, the better the talk will go for you.

Essentially, you have a story to tell, but that does not mean you are [story telling](#storytelling). It means that your presentation will require you to talk continuously for your allotted period of time, and that the sentences must follow on from each other in a logical narrative; i.e. a story.

## So where do you start?

### Here are some simple rules to help guide you to build your presentation:

- **One slide per minute**: However many minutes you have to present, that’s your total number of slides. Don’t be tempted to slip in more.
- **Keep the format clear**: There are lots of templates available to use, but you’d do best to keep your presentation very clean and simple.
- **Be careful with animations**: You can build your slide with animations (by adding images, words or graphics). But do not flash, bounce, rotate or roll. No animated little clipart characters. No goofy cartoons – they’ll be too small for the audience to read. No sounds (unless you are talking about sounds). Your audience has seen it all before, and that’s not what they’ve come for. They have come to hear about your research proposal.
- **Don’t be a comedian*: Everyone appreciates that occasional light-hearted comment, but it is not stand-up. If you feel that you must make a joke, make only one and be ready to push on when no-one reacts. Sarcasm simply won’t be understood by the majority of your audience, so don’t bother: unless you’re a witless Brit who can’t string three or more sentences together without [in which case you have my empathy].

### A formula for presenting a proposal

1. You need a title slide (with your name, that of your advisor and institution)
2. Several slides of introduction
  + that put your study into the big picture
  + explain variables in the context of existing literature
  + explain the relevance of your study organisms
  + give the context of your own study
3. Your aims and hypotheses
4. Methods and Materials
  + Images of apparatus or diagrams of how apparatus are supposed to work. If you can’t find anything, draw it simply yourself.
  + Your methods can be abbreviated but the methods are important for a proposal, especially the numbers of replicates and the variables that you plan to measure from them. 
  + Analyses are important. Make sure that you understand how they work, otherwise, you won’t be able to present them to others. Importantly, explain where each of the variables that you introduced, and explained how to measure, fit into the analyses. There shouldn’t be anything new or unexpected that pops up here.
5. Expected results
6 like to see what the results might look like, even if you have to draw graphs with your own lines on it. Use arrows to show predictions under different assumptions.
7. Budget
8. Timeline

## Know your story first, and then make your presentation

@@

Remember that you don't need to include every detail in your slides or your talk. If the audience can follow your story, but wants to know the details at the end, then they can ask questions about the details. Indeed, you can tell your audience precisely this as a way of side-stepping chunks of (especially boring) methodologies.

@@

## Slide layout

1. Your aim is to have your audience listen to you, and only look at the slides when you indicate their relevance. 
1. You’d be better off having slides without words, then your audience will listen instead of trying to read. As long as they are reading, they aren't listening. Really try to limit the words you have on any single slide (<30). Don’t have full sentences, but write just enough to remind you of what to say and so that your audience can follow when you are moving from point to point.
1. Use bullet pointed lists if you have several points to make (Font 28 pt)
1. If you only have words on a slide, then add a picture that will help illustrate your point. This is especially useful to illustrate your organism. At the same time, don’t have anything on a slide that has no meaning or relevance. Make sure that any illustration is large enough for your audience to see and understand what it is that you are trying to show.
1. Everything on your slide must be mentioned in your presentation, so remove anything that becomes irrelevant to your story when you practice.
1. Tables: you are unlikely to have large complex tables in a presentation as presenting raw data or small words in a table is a way to lose your audience. Make your point in another way.
1. Use citations (these can go in a smaller font: 20 pt). I like to cut out the title and authors of the paper from the pdf and show it on the slide.
1. If you can, have some banner that states where you are in your presentation (e.g. Methods, or 5 of 13). It helps members of the audience who might have been daydreaming.

@@

## Practice, practice, practice

1. It can’t be said enough that you must practice your presentation. Do it in front of a mirror in your bathroom, or in front of your friends. It's the best way of making sure you'll do a good job.
1. If you can't remember what you need to say, write flash cards with prompts. Include the text on your slide and expand. When you learn what’s on the cards, relate it to what’s on the slide so that you can look at the slides and get enough hints on what to say. Don’t bring flashcards with you to your talk. Instead be confident enough that you know them front to back and back to front.
1. Practice with a pointer and slide advancer (or whatever you will use in the presentation). You should be pointing out to your audience what you have on your slides; use the pointer to do this.
1. Avoid taking anything with you that you might fiddle with.

### 2021-07-20 2.22-transparency.Rmd
Add files via upload
# After copy edits

In this book, I have tried to consistently encourage you toward transparent and open practices in science. Here my aim is to introduce this topic and provide an overview of the main areas in which you can currently make a difference by opening up your research. As the Centre for Open Science explains (COS: [see here](https://youtu.be/9YuNGB3vNOw)), this will take a shift in the culture of the scientific community, which is why you need to understand and adopt a transparent approach from the outset of your research career. There are much better and more comprehensive guides and online resources so I encourage you to look through the literature cited here. Although I advocate hard for the COS, please be aware that this is not the only set of guidelines (see also [recent moves by the Public Library of Science](https://plos.org/open-science/preregistration/)) and [Peer Community In](https://peercommunityin.org/).

@@

You will spend a considerable amount of time at the beginning of your PhD studies planning what you want to do. In many institutions, this will take the form of a formal proposal. It will be agreed with your advisor, and may well pass the inspection of a committee. You will put a lot of effort into reading the literature in order to ask the best hypotheses possible. You will design your experiments with rigor and control, and potentially redesign them after your advisor and committee comment. The effort put into your proposal is totally disproportionate if it’s never looked at again. Yet, this document is of historical importance, because it says what you think before ever doing the experiment and collecting or analysing the data. Thus, it can in future prove that you were not conforming to confirmation bias, for example by [HARKing](TypeI.html): rewriting your hypothesis after getting your results in order to get a significant result [@kerr1998harking; @forstmeier2017detecting].

Confirmation bias is a problem in science because of the way that science is published. In brief, articles for journals with higher impact are regularly selected based on significant results. If you don’t have that significance, they are unlikely to want to take your manuscript. For this reason, many scientists have sought to have significant results to report, and this is called confirmation bias. Confirmation bias is bad because it violates the assumption that we are answering the hypothesis that we started with, or it could cause scientists to manipulate their data until a significant result is achieved. For example another form of confirmation bias is p hacking: repeating tests with different approaches in order to a significant result. Rubin [-@rubin2020does] gives a good list and set of explanations. As there are a lot of known ways in which researchers have been thought to deliberately or accidentally report false-positive findings, one solution can be archiving your intentions, referred to as preregistration [@forstmeier2017detecting] see Figure \@ref(fig:preregistration). If you register your proposal (or any research plan), you can present this historical document to a journal (probably 4 to 5 years later) to show that you have done what you planned to do (see [webinar on preregistration here](https://youtu.be/8QK2-udwoK8)).

@@

What if new analyses appear during the period, or you are forced to change your experimental protocol. Certainly, most analytical software will be updated over the course of your studies, and some might be superseded. None of this is a real problem to your preregistered content. Logging the software that you intend to use will demonstrate the approach and type of analyses that you intend to take. While it is unlikely that you will ever be held to account for minor changes to equipment or protocol, things do change along the way. It doesn’t mean that you won’t be able to report your results, or that your research won’t be viable. But it does mean that you will need to be transparent about why it changed. For this reason, it is a good idea to document the changes to your proposed research plan and why they happened. It is surprisingly easy to forget! There are some great tools on different platforms for adding this information, together with a timestamp so that it’s clear when it was done.

@@

Although at first sight, preregistration appears to confine you to only testing ideas that you had before you started a study, actually the opposite is true. When you preregister your proposal (or research plan) it places a time-stamp and therefore a historical trail on your ideas. If as you go along with your study you gain new insight and ideas, you can register these with their own time-stamp. When it comes to analysing your data, you use a separate section labelled “exploratory analyses”. You can then apply post-hoc rules to these findings, which will not stop you from reporting them, but gets around the awkwardness of [HARKing](TypeI.html). This serves to reinforce the distinction between prediction and postdiction.

@@

It is probably too early to tell [@rubin2020does], but it is certainly a good place to start [@nosek2018preregistration]. The more researchers know and subscribe to [transparency](transparency2.html) in their research, the more it will shift the culture in science for the better [@forstmeier2017detecting].However, there are more biases existing in science, and the system needs buy-in from stakeholders to promote equity by elimination of bias.

A new initiative from [Peer Community In](https://peercommunityin.org/) is the possibility of submitting to their [Registered Reports](https://rr.peercommunityin.org/), which goes much further towards removing the confirmation bias. The Registered Report (RR) is in effect the registration of a proposal (i.e. preregistration) with review. If the RR is approved by reviewers then the study is, in principle, given the green light for publication whether or not the hypothesis posed is accepted or rejected. I say "in principle" because those same reviewers are shown the ms again once the results are in. They need to check that the methods proposed were followed, the analyses were conducted in the same way they were proposed, and that the conclusions are justified by the results. In terms of figure \@ref(fig:preregistration), Peer Community In are offering to organise the two yellow review arrows. In addition, there are a bunch of journals that have already signed up to accept RRs that are signed off after completion (notable among these is [PeerJ](www.peerj.com)). To me, this represents an important step in the right direction toward transparency, and the elimination of confirmation bias. What would be great to see is the number of conventional journals sign up with RRs based on the quality of the study design and execution, and the concomitant abandonment of Impact Factor as a driving force in publishing.

@@

When choosing where to archive your proposal (or any of your data, analyses, etc.) there are lots of platforms to choose from: [Bitbucket](https://bitbucket.org/product), [Figshare](https://figshare.com/), [Github](https://github.com/), [OSF](https://osf.io/), [Zenodo](https://zenodo.org/) and the list will undoubtedly grow. Making a decision about what you are going to use now may not require that you stick with this same platform for you entire career, but there are some things that you should consider:

@@

The platform you choose should work for you (rather than having you work for it). If you are someone who loves to have everything ordered and organised, then you’ll love seeing this all laid out. If you aren’t, then these platforms are going to be a massive help to getting all of your plans sorted. Make updating your platform a habit. For example, you could make sure that notes taken during meetings with your advisor on different projects are logged onto the platform. This way you both have a record of what decision was made when. Remember that you can choose what you make accessible to the outside world.

@@

There are a whole lot more transparency criteria that you will need to be aware of later on in your PhD when it comes to publishing. Becoming familiar with the entire process now will be to your advantage, so I encourage you to read more about this topic. Sullivan et al [-@sullivan2019open] provide a nice overview about how to get started, but be sure to consult documentation at [OSF](https://osf.io/).

>>>>

In this book, I consistently encourage you toward transparent and open practices in science. Here my aim is to introduce this topic and provide an overview of the main areas in which you can currently make a difference by opening up your research. As the Centre for Open Science explains (COS: [see here](https://youtu.be/9YuNGB3vNOw)), this will take a shift in the culture of the scientific community, which is why you need to understand and adopt a transparent approach from the outset of your research career. There are much better and more comprehensive guides and online resources, so I encourage you to look through the literature cited here. Although I advocate hard for the COS, please be aware that this is not the only set of guidelines (see also [recent moves by the Public Library of Science](https://plos.org/open-science/preregistration/) and [Peer Community In](https://peercommunityin.org/)).

@@

You will spend a considerable amount of time at the beginning of your PhD studies planning what you want to do. In many institutions, this will take the form of a formal proposal. It will be agreed with your advisor, and may well pass the inspection of a committee. You will put a lot of effort into reading the literature in order to ask the best hypotheses possible. You will design your experiments with rigor and control, and potentially redesign them after your advisor and committee comment. The effort put into your proposal is totally disproportionate if it’s never looked at again. Yet, this document is of historical importance because it says what you think before ever doing the experiment, and collecting or analysing the data. Thus, it can in future prove that you were not conforming to confirmation bias, for example by [HARKing](#TypeI): rewriting your hypothesis after getting your results in order to get a significant result [@kerr1998harking; @forstmeier2017detecting].

Confirmation bias is a problem in science because of the way that science is published. In brief, articles for journals with higher impact are regularly selected based on significant results. If you don’t have that significance, they are unlikely to want to take your manuscript. For this reason, many scientists have sought to have significant results to report, and this is called confirmation bias. Confirmation bias is bad because it violates the assumption that we are answering the hypothesis that we started with, or it could cause scientists to manipulate their data until a significant result is achieved. For example another form of confirmation bias is [p hacking](#TypeI): repeating tests with different approaches in order to obtain a significant result. Rubin [-@rubin2020does] gives a good list and set of explanations. As there are a lot of known ways in which researchers have been thought to deliberately or accidentally report false-positive findings, one solution can be archiving your intentions, referred to as preregistration [@forstmeier2017detecting] see Figure \@ref(fig:preregistration). If you register your proposal (or any research plan), you can present this historical document to a journal (probably 4 to 5 years later) to show that you have done what you planned to do (see [webinar on preregistration here](https://youtu.be/8QK2-udwoK8)).

@@

What if new analytical methods appear during the period, or you are forced to change your experimental protocol? Certainly, most analytical software will be updated over the course of your studies, and some might be superseded. None of this is a real problem to your preregistered content. Logging the software that you intend to use will demonstrate the approach and type of analyses that you intend to take. It is unlikely that you will ever be held to account for minor changes to equipment or protocol as things do change along the way. It doesn’t mean that you won’t be able to report your results, or that your research won’t be viable. But it does mean that you will need to be transparent about why it changed. For this reason, it is a good idea to document the changes to your proposed research plan and why they happened. It is surprisingly easy to forget! There are some great tools on different platforms for adding this information, together with a timestamp so that it’s clear when it was done.

@@

Although at first sight, preregistration appears to confine you to only testing ideas that you had before you started a study, actually the opposite is true. When you preregister your proposal (or research plan) it places a time-stamp and, therefore, a historical trail on your ideas. If as you go along with your study you gain new insight and ideas, you can register these with their own time-stamp. When it comes to analysing your data, you use a separate section labelled 'exploratory analyses'. You can then apply post-hoc rules to these findings, which will not stop you from reporting them, but gets around the awkwardness of [HARKing](#TypeI). This serves to reinforce the distinction between prediction and postdiction.

@@

It is probably too early to tell [@rubin2020does], but it is certainly a good place to start [@nosek2018preregistration]. The more researchers know and subscribe to [transparency](transparency2.html) in their research, the more it will shift the culture in science for the better [@forstmeier2017detecting]. However, there are more biases existing in science, and the system needs buy-in from stakeholders to promote equity by elimination of bias.

A new initiative from [Peer Community In](https://peercommunityin.org/) is the possibility of submitting to their [Registered Reports](https://rr.peercommunityin.org/), which goes much further towards removing the confirmation bias. The Registered Report (RR) is in effect the registration of a proposal (i.e. preregistration) with review. If the RR is approved by reviewers then the study is, in principle, given the green light for publication whether or not the hypothesis posed is accepted or rejected. I say 'in principle' because those same reviewers are shown the manuscript again once the results are in. They need to check that the methods proposed were followed, the analyses were conducted in the same way they were proposed, and that the conclusions are justified by the results. In terms of Figure \@ref(fig:preregistration), Peer Community In are offering to organise the two yellow review arrows. In addition, there are a bunch of journals that have already signed up to accept RRs that are signed off after completion (notable among these is [PeerJ](www.peerj.com)). To me, this represents an important step in the right direction toward transparency, and the elimination of confirmation bias. What would be great to see is the number of conventional journals sign up with RRs based on the quality of the study design and execution, and the concomitant abandonment of Impact Factor as a driving force in publishing.

@@

When choosing where to archive your proposal (or any of your data, analyses, etc.), there are lots of platforms to choose from: [Bitbucket](https://bitbucket.org/product), [Figshare](https://figshare.com/), [Github](https://github.com/), [OSF](https://osf.io/), [Zenodo](https://zenodo.org/) and the list will undoubtedly grow. Making a decision about what you are going to use now may not require that you stick with this same platform for your entire career, but there are some things that you should consider:

@@

The platform you choose should work for you (rather than having you work for it). If you are someone who loves to have everything ordered and organised, then you’ll love seeing this all laid out. If you aren’t, then these platforms are going to be a massive help to getting all of your plans sorted. Make updating your platform a habit. For example, you could make sure that notes taken during meetings with your advisor on different projects are logged onto the platform. This way, you both have a record of what decision was made when. Remember that you can choose what you make accessible to the outside world.

@@

There are a whole lot more transparency criteria that you will need to be aware of later on in your PhD when it comes to publishing. Becoming familiar with the entire process now will be to your advantage, so I encourage you to read more about this topic. Sullivan et al. [-@sullivan2019open] provide a nice overview about how to get started, but be sure to consult documentation at [OSF](https://osf.io/).

### 2021-07-20 2.23-funding.Rmd
Add files via upload
# After copy edits

## Generating funding for your PhD research {#funding}

To be honest, writing a funding proposal is an art in itself and should be the subject of an entirely different book written by somebody else. What is written here is only really scratching the surface so I suggest that if generating funding for your PhD research is going to be a large part of your work then you should look for another book.

### Funding databases

Funding is one of the most important aspects of doing science, and something that different emphasis is placed on in different parts of the world. In North America, in particular, graduate students are expected to be able to demonstrate that they are able to raise their own funds, as this is expected of them in their jobs as academics. No matter where you are, your CV will be greatly improved by showing prospective employees (or labs) that you can generate your own funding. North America has a lot of opportunities to apply for funding for all sorts of reasons. There are less opportunities elsewhere, but the pool of people applying is also smaller. There are now so many opportunities, that several databases exist to help you find appropriate funding for your particular situation.

@@

### Reasons you might want to apply for funding:

- To improve your CV. Even if it’s only a small amount of funding that you apply for, it will make your CV look better. You might also want to search for prizes. Academic prizes carry both money and that feel good, look good feeling that CVs need.
- Your project is unfunded. If you are completely unfunded, or you have a bursary but no running expenses, then you are going to need money to do your work. The more work (particularly field work) that you want to do, the more money you’ll need to raise.
- Your project is funded, but you want to do more. If you want to do a lot extra (like side projects or paying assistants to collect extra data) then all of this is possible if you can raise some more money to do it. 
- You want to attend a conference or workshop. There are great opportunities for travelling around the world, but they cost money and international conferences are often very expensive.
Publishing in Open Access journals. I find the idea of putting cash into the pockets of publishers abhorrent, but you may have little choice. There are some opportunities to get funding for OA publishing. 
- It is clear that without making an application, you won’t get any funding. But where do you start?
Databases. There are many databases, but here we’ll mention 3 that are easy to use.

#### Mendeley:https://www.mendeley.com/ 
This is probably my favorite. It’s easy to use and apply or remove filters. You can use the same login that you have for the referencing software and SCOPUS.

#### Open 4 Research: https://www.open4research.eu 
For this you’ll need an academic email address to register, but you’ll get access to their research database. It is nice and logical to use, and you’ll find local and international funding opportunities.

#### Research Professional:https://www.researchprofessional.com/ 
You’ll need to create a login for this site, although you might get an in with your university address. This provides you access to what could well be the same database as those above. This is a slick database and relatively easy to use.

#### Opportunities in your department or societies:
Probably the most likely place to get funding is where you already have an “in” (where you are already known). This will include professional societies where you are a member, or your department or university. These places also have prizes, so it’s good that you know what is on offer in order to benefit the most.

>>>>

# Generating funding for your PhD research {#funding}

To be honest, writing a funding proposal is an art in itself and should be the subject of an entirely different book. What is written here is only really scratching the surface, so I suggest that if generating funding for your PhD research is going to be a large part of your work then you should look for an additional book.

## Funding databases

Funding is one of the most important aspects of doing science, and something that different emphasis is placed on in different parts of the world. In North America, in particular, some graduate students are expected to be able to demonstrate that they are able to raise their own funds, as this is expected of them in their jobs as academics. No matter where you are, your CV will be greatly improved by showing prospective employees (or labs) that you can generate your own funding. North America has a lot of opportunities to apply for funding for all sorts of reasons. There are less opportunities elsewhere, but the pool of people applying is also smaller. There are now so many opportunities, that several databases exist to help you find appropriate funding for your particular situation.

@@

## Reasons you might want to apply for funding:

- To improve your CV. Even if it’s only a small amount of funding that you apply for, it will make your CV look better. You might also want to search for prizes. Academic prizes carry both money and that feel good, look good feeling that CVs need.
- Your project is unfunded. If you are completely unfunded, or you have a bursary but no running expenses, then you are going to need money to do your work. The more work (particularly field work) that you want to do, the more money you’ll need to raise.
- Your project is funded, but you want to do more. If you want to do a lot extra (like side projects or paying assistants to collect extra data) then all of this is possible if you can raise some more money to do it. 
- You want to attend a conference or workshop. There are great opportunities for travelling around the world, but they cost money and international conferences are often very expensive.
- Publishing in Open Access journals. I find the idea of putting cash into the pockets of publishers abhorrent, but you may have little choice. There are some opportunities to get funding for OA publishing. 
- It is clear that without making an application, you won’t get any funding. But where do you start?
Databases. There are many databases, but here are 3 that are easy to use.

### Mendeley:https://www.mendeley.com/ 
This is probably my favorite. It’s easy to use and apply or remove filters. You can use the same login that you have for the referencing software and SCOPUS.

### Open 4 Research: https://www.open4research.eu 
For this you’ll need an academic email address to register, but you’ll get access to their research database. It is nice and logical to use, and you’ll find local and international funding opportunities.

### Research Professional:https://www.researchprofessional.com/ 
You’ll need to create a login for this site, although you might get an in with your university address. This provides you access to what could well be the same database as those above. This is a slick database and relatively easy to use.

### Opportunities in your department or societies:
Probably the most likely place to get funding is where you already have an 'in' (where you are already known). This will include professional societies where you are a member, or your department or university. These places also have prizes, so it’s good that you know what is on offer in order to benefit the most.

### 2021-07-20 2.24-fear.Rmd
Add files via upload
# After copy edits

## Fear of submitting written work {#fear}

Many people feel nervous of handing in their written work, and feeling a little nervous is good. It shows that you care deeply about your work. However, when it gets so bad that you can't hand work in any more, then something has gone wrong. It is possible that you are suffering from **impostor syndrome**. This chapter is to help you overcome your fear of handing in your written work.

### What is impostor syndrome? {#impostorsyndrome}

@@

- Are you fearful that your work won’t be well received? 
- Is it really up to the standards that are required?
- Could you do better if you just spent some more time?

@@

### Think of it this way

@@

### What can you do to help yourself overcome the fear of submitting written work?

1. Give it to a friend or colleague to read
1. Remember that most of what you write should be understandable to the majority of people who can read (think of articles in The Conversation as a reasonable reading/understanding level). This means that you can give your written work to fellow postgraduates and postdocs and ask for feedback. 
1. Annotate your text with places where you are particularly unsure.
If there’s a certain part that you are struggling with, annotate it (add comment in word) and point out that you are struggling with this particular section
1. Ask for a meeting with your advisor
You can sit down together with your advisor and discuss the points where you are uncertain before handing in the work. Or, after you’ve written it you can ask for a session when you are given verbal feedback
1. Produce a checklist
If you specifically worry that there may be errors in what you write (grammatical, spelling, plagiarism), then make a checklist that you can tick off prior to submitting. Once your check list is done, don’t mess with the written work again (or you could add more errors), just hand it in!
1. Set a deadline for yourself
If you don’t already have one, having a set of deadlines that you give yourself to give your writing to work to colleagues and hand in to your advisor. If you know that you aren’t good with deadlines, share them with as many people as you can!
1. Provide yourself with a reward for submitting your work. Rewards are a really simple way of helping you to do things. They help simplify otherwise apparently complex fears. 
1. Tell your advisor about your fears
There’s nothing like honesty. Your advisor may be able to cut you some slack, or might sit down with you and look at how the two of you can overcome this difficulty.
If you have more than one advisor, there may be one who you are more confident to read your work, and you can suggest that reading is done in series (instead of in parallel - actually I’d advise this).
1. Talk to your advisor about what really gets you the most upset. If you can’t do this face to face, then you could annotate it in a reply to their comment. The chance is that your advisor doesn’t know how upsetting it is and you’ll be helping them in their future interactions with students. 
1. Ask your advisor about their fear of handing in and get them (and others in your lab) to share their stories. You might find that you have common ground to start sharing how these problems can be overcome.

@@

>>>>

# Fear of submitting written work {#fear}

Many people feel nervous of handing in their written work, and feeling a little nervous is good. It shows that you care deeply about your work. However, when it gets so bad that you can't hand work in any more, then something has gone wrong. It is possible that you are suffering from **impostor syndrome**.

## What is impostor syndrome? {#impostorsyndrome}

@@

- Are you fearful that your work won’t be well received (Figure \@ref(fig:conflicted))? 
- Is it really up to the standards that are required?
- Could you do better if you just spent some more time?

@@

## Think of it this way

@@

## What can you do to help yourself overcome the fear of submitting written work?

1. **Give it to a friend or colleague to read**
1. **Remember that most of what you write should be understandable to the majority of people** around you. This means that you can give your written work to fellow postgraduates and postdocs and ask for feedback. 
1. **Annotate your text with places where you are particularly unsure**.
If there’s a certain part that you are struggling with, annotate it (add comment) and point out that you are struggling with this particular section
1. **Ask for a meeting with your advisor**. You can sit down together with your advisor and discuss the points where you are uncertain before handing in the work. Or, after you’ve written it you can ask for a session when you are given verbal feedback
1. **Produce a checklist**. If you specifically worry that there may be errors in what you write (grammatical, spelling, plagiarism), then make a checklist that you can tick off prior to submitting. Once your check list is done, don’t mess with the written work again (or you could add more errors), just hand it in!
1. **Set a deadline for yourself**. If you don’t already have one, having a set of deadlines that you give yourself to give your writing to colleagues and hand in to your advisor. If you know that you aren’t good with deadlines, share them with as many people as you can!
1. **Provide yourself with a reward for submitting your work**. Rewards are a really simple way of helping you to do things. They help simplify otherwise apparently complex fears. 
1. **Tell your advisor about your fears**. There’s nothing like honesty. Your advisor may be able to cut you some slack, or might sit down with you and look at how the two of you can overcome this difficulty.
If you have more than one advisor, there may be one who you are more confident to read your work, and you can suggest that reading is done in series (instead of in parallel - actually, I’d advise this).
1. **Talk to your advisor about what really gets you the most upset**. In case it's something that your advisor does that makes you anxious. If you can’t do this face to face, then you could annotate it in a reply to their comment. The chance is that your advisor doesn’t know how upsetting it is and you’ll be helping them in their future interactions with students. 
1. **Ask your advisor about their fear of handing in** and get them (and others in your lab) to share their stories (for example at a lab meeting). You might find that you have common ground to start sharing how these problems can be overcome.

@@

## When is it good enough to submit to my advisor? {#goodenough}

Once you've read and revised the draft text three times yourself, and you feel that you can't really improve it any more, hand it over. Personally, I need to wait a day or more between drafts when I work on something else, or do some reading. I find that it really helps to think about writing while not writing. Run through the arguments in your head when you are doing something else. That could be time in the gym, out running, cycling or swimming. Or talk through the logic of your argument with a friend or colleague while having coffee. You’ll find that spending time thinking away from sitting in front of your word-processor will be really valuable in promoting productivity once you sit down again.

If you are [fearful of handing in](#fear) your work, share it with others to give you confidence. Hand it to an office mate or other friend first. Your reader shouldn't have to be an expert in your field, but only needs to have a loose grasp on scientific writing to follow any paper. As a guide, any recent graduate of a biological sciences degree (BSc) should be able to understand. This makes it easy to find lots of potential readers for your manuscript before handing it in.
